A Particular Appetite: Cosmological Hydrodynamic Simulations of Preferential Accretion in the Supermassive Black Holes of Milky Way Size Galaxies

### 2016-03-30 ms.tex
Added some text and making sure all recent updates are accounted for

%\documentclass[]{emulateapj}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

@@

\citep[for example; ][at the end of the line]{Bellovary2010,Tremmel2015,Fu2008}

 \S\ref{sec-intro}

Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies. \citep{Kormendy2013} [OTHERS?] In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence. \citep{Volonteri2012} [GET OBS REFS] The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center [REFS]; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together. [ADD REFS FROM REVIEWS; + \citep{Fu2008}]

[Note to self: Make sure paper thoroughly discusses what we think we KNOW about growth/evolution and what is still being DEBATED]

The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects. \citep{Kormendy2013} A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge. % For my thesis: A prominent trend appears as SMBHs tend to scale with the spheroidal center of their host galaxies; i.e. less massive SMBH reside in galaxies with less disperse bulges, and more massive SMBH live in galaxies with larger velocity dispersions in their bulges. 
The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass. (\cite{Mcconnell2013}; \cite{Kormendy2013}; \cite{Merritt2001}) Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where over massive BHs may reside. [Vanden Bosch, Emsellem, Prija, maybe Volonteri?] However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation. [Micic, previous Kelly student (ask Kelly, couldnt read this word), Volonteri] One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges. [Mick and others] These large, active mergers are thought to create feedback from the SMBH which affects the structure of the galaxy. [REFS]

%McConnell and Ma have the prettiest M-sigma relation, but there are two camps: Kormendy and Ferrarese & Merritt who must both be cited.
%Check with Kelly: Which Vanden, Bosch, Emsellem, and Prija papers she would recommend.

[CITE FOR THEORY: Springel and Dimatteo; cite when we discuss why m-sigma happens]

@@

The M$_{BH}$-bulge luminosity relation was first implied by the work of Dressler \& Richstone 1988 and Dressler 1989 first proposed the correlation while it was first illustrated by Kormendy 1993a. The M$_{BH}$-bulge mass relation followed and was determined via ground based observations by Magorrian 1998 and was around M$_{BH}$ ~ 0.005 M$_{bulge}$; however, this relation was characterized by a lot of scatter and its reliability waned due to selection biases.  Follow up examinations by others using HST observations constrained the M$_{BH}$/M$_{bulge}$ fraction to between about 0.0013 and 0.0023 (Merritt \& Ferrarese 2001; cf. McLure \& Dunlop 2002 and Marconi \& Hunt 2003, respectively).

Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN. The large influx of material due to tidal torques from the merger cause bursts of star formation and helps funnel gas directly into the center where the SMBH resides. (Hopkins 2010 canonical on tidal torques/ang mom, Richards 06, Reddy 08) Additionally, the most massive, highest-luminosity AGN (i.e. quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred. [REFS] Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes. [REFS]

	In many less massive AGN [REFS], however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence.  [Ryan 2007 (Seyfert 1, smaller than MWG), Hicks 2013 (Seyfert and quiescent galaxies)]  It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers. (Schawinski 2011; Kocevski 2012) Nevertheless, some evidence suggests (Governato 2009) that disturbed galaxies may reform a disk quickly, even if their history is characterized by many mergers. More recently, Triester (2012) has suggested that only the highest luminosity AGN require fueling via major mergers, an effect which seems to scale with luminosity rather than redshift. They found that ~90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium. Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs. [REFS; maybe Graham, or K\& Ho]

	Smooth accretion of cold flow gas seems a likely candidate for fueling these low mass galaxies. Filaments of unshocked gas may fuel until the galaxy halo reaches a total (virial) mass near 10$^{11} M_{\odot}$ [DiMatteo(maybe), Keres 05, Brooks 2007; maybe Dekel (look at who cites Keres and Brooks in ADS]; once in more massive halos, the gas will shock heat to the virial temperature of the halo.  % For my thesis: The cold flow filaments that feed thses galaxies are dependent on the galaxy's mass. Smoothly accreted gas will fuel through cold flow filaments until the galaxy halo reaches a a mass near 10$^{11} M_{\odot}$. Once the galaxy's mass is greater than this threshold, the mass will reach the virial radius of the halo and the rapid increase in temperature within the radius causes the gas to shock as its temperature quickly increases.

It is known that galaxy hosts grow through different channels that depend on mass, environment, and interaction history; therefore, we would like to understand how these different galaxy evolutionary paths translate into different SMBH fueling mechanisms, and to see if it affects the state of fueling gas flowing into the SMBH itself. Therefore, we will also discuss the fueling mechanisms which also vary between galaxies of similar mass due to different merger and formation histories.

	 In this paper, we discuss the gas accretion history within two galaxy simulations that appear similar at z = 0 but have very different merger histories. Our "active" galaxy, h258, has a history characterized by many major mergers, while our "quiet" galaxy, h277, has a quiescent history dominated by cold flow accretion and few minor mergers. These galaxies look quite similar at z=0, and have many of the same properties as the Milky Way including M$_{vir}$ (mass within the virial radius), stellar mass, and v$_{circ}$ (circular velocity). However, without a deeper examination, we might not realize they have such varying merger histories. Milky Way-type galaxies host SMBHs on the order of 10$^6$ M, which are likely the most common type of massive black hole, yet little is known about them or how they may grow. By examining the feeding mechanisms of these galaxies, as well as what type of gas feeds their central SMBHs, we will be able to compare the accretion rates between h258 and h277 to determine which accretion methods dominate within the central regions of these Milky Way-size galaxies.

	\cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both build up galaxies, no particular method was more adept at feeding the SMBH at their centers. Using a similar method as \cite{Bellovary2013}, this work compares the fueling mechanisms between two MW mass galaxies and the accretion affecting each of their SMBHs. We will compare the BH fractions and halo fractions between and within the galaxies to look for clues about SMBH preferential feeding within these MW-size galaxies and how their histories lead to galaxies with such similar structure.

@@

@@

	The cosmological simulations have been run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline (Stadel 2001; Wadsley 2004). \citep{Wadsley2004} Prescriptions for star formation, supernova feedback (Stinson 2006), metal diffusion (Shen 2010), and MBH formation, feedback, and accretion \citep{Bellovary2010} are included within Gasoline. Each simulations assumes a WMAP cosmological model (Spergel 2007), Kroupa initial mass function (Kroupa 2001), and a uniformly distributed ultraviolet background (Haardt \& Madau 1996). Gasoline simulated galaxies are shown to lie conform with the observed Tully-Fisher relation (Governato 2009), the size-luminosity relation (Brooks 2011), and the mass-metallicity relation (Brooks 2007), in addition to having realistic matter distributions and baryon fractions (Governato 2010; Guedes 2011). Primordial cooling and a low-temperature extension to the cooling curve is used to trace metals (Bromm2001). Gas is allowed to reach a minimum temperature of ~100 K, though cooling via molecular hydrogen or metals is not included. The aforementioned works have previously demonstrated that realistic galaxy models can be obtained without the use of these advanced features. (Christensen2012, in addition). Though these previous works have not included AGN feedback or its effects, for small to moderate mass galaxies (like those of previous and current studies) our research shows their central supermassive black holes have little affect on the global properties of their hosts and only directly impacts the central region of their galaxy. Therefore, we are confident these simulations are in good accordance with the broad range of properties in current galaxy observations.

	We have examined two simulations, each of a uniform volume cube with 50 Mpc sides. [Volume normalization technique?] The main halo of each simulation results in a Milky Way-size spiral galaxies with z=0 masses between 6--8 $\times$ 10$^{11}$  M$_{\odot}$. The simulations each have a force resolution of 300 pc [Note: I have 300 written in my research notebook, but B13 says 260. The notes I have are the ones I took so AAS so maybe that's a rounded up value?]. The gas, dark matter, and star particles have masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.  [Jillian's paper includes a table of simulation properties. Should I create one as well? I feel like yes.]

	The simulation includes stochastically modeled star formation, including a density threshold (2.5 amu cm$^-3$) for gas particles above which they become eligible to form stars; the gas must also be below a temperature threshold of 10$^4$ K. Additionally, we utilize a star formation efficiency parameter of c$^*$ $=$ 0.1. Our supernova feedback energy is E$_SN$ $=$ 1 $\times$ 10$^51$ erg and, using the blastwave equations from McKee \& Ostriker (1977), the energy is passed to surrounding particles within a calculated radius. The equation also determine how long the cooling is shut off for heated particles. These parameters and resolution choice allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation. (Moster 2010; Munshi 2013) We are confident with these criteria and restraints that we reasonably represent growth in the galaxy and its SMBH. [Note: I did change the variables to h258/h277 values. Cstar is the same, but Esn was larger.]

	%Like the star formation, seed black hole formation is modeled stochastically but requires the additional stipulation that black holes must form from zero-metallicity gas. A gas particle that has zero-metallicity and also meets the requirements for star formation will have a probability, $\chi_{seed}$, that it will become a black hole. The resulting black hole will maintain the same mass as its parent gas particle (2 $\times$ 10$^5$) M$_{\odot}$. We set  $\chi_{seed}$ $=$ 0.1 to achieve adequate MBH occupation fractions, without an over production of merger events between MBHs. This circumvents the Soltan arguments wherein mergers alone feed MBHs almost entirely without allowing for accretion growth. This method is nearly consistent the theories of direct collapse black holes from gas (Couchmann \& Rees 1986, Abel 2002, Bromm \& Larson 2004) and Population III star black hole formation (Loeb \& Rasio 1994, Eisentstein \& Loeb 1995, Koushiappas 2004, Begelmann 2006, Lodato \& Natarajan 2006). Utilizing this requirement, we ensure that black hole formation ceases at high redshift, since at this time the interstellar medium (ISM) has become overwhelmed with metals due to supernova remnants. Black holes are not fixed within their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy.  Multiples may also form within the same halo. Dark matter particles have slightly larger masses than black holes to tamper the effects of artificial two-body scattering and to keep the black holes in the center of their dark matter host particles. \\

	%There are still many uncertainties regarding the formation of black holes "seeds" and their evolution into the SMBHs we see at the centers of galaxies. Neverthless, we do know there must be some method driving their quick transformation from seeds to quasars that can be seen at z ~ 6. [Fan 2001] We assume the method of direct collapse from pristine, low metallicity gas to create our seed BHs. [Begelman 2006] While this method allows the BH formation process to remain physically motivated, the choice of BH seeding method is not terribly important as our focus remains on the dynamic evolution of the seeds, which is not dependent on their initial mass (10$^5$ M$_{\odot}$ for the direct collapse scenario and 100 M$_{\odot}$ for the first stars [Include latter half of sentence? Is that method used?]). These heavier BH seeds have a dynamical friction time longer than the Hubble time, due to local densities. BH seeds form if their parent gas particle match the criteria required for star formation] and also maintain zero metallicity. [Stinson 2006 for star formation details] A probability of $\chi_{seed}$ = 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle. This probability was chosen to match the predicted occupation probability of BH seeds at z ~ 3. [Volonteri 2008] BH seed formation ends at z ~ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae. The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation. Should two BHs form within a softening length, the BHs merge into one with a mass equal to the sum of both BH seed masses. BHs formation is dependent only on their local environment, neglecting any large-scale properties of the host halo. BHs are also allowed to move within their halos, if influenced by external forces, rather than being artificially pinned to the centers of their host halos. Nevertheless, BHs are kept near their host centers by choosing dark matter particles masses in high-resolution regions to be on the same order as gas particle masses which minimizes two-body interactions. [Bellovary et. al. 2010]\\

	There are still many uncertainties regarding the formation of black holes "seeds" and their evolution into the SMBHs we see at the centers of galaxies. Neverthless, we do know there must be some method driving their quick transformation from seeds to quasars that can be seen at z ~ 6. [Fan 2001] We assume the method of direct collapse from pristine, low metallicity gas to create our seed BHs. [Begelman 2006] While this method allows the BH formation process to remain physically motivated, the choice of BH seeding method is not terribly important as our focus remains on the dynamic evolution of the seeds, which is not dependent on their initial mass (10$^5$ M$_{\odot}$ for the direct collapse scenario and 100 M$_{\odot}$ for the first stars [Include latter half of sentence? Is that method used?]). These heavier BH seeds have a dynamical friction time longer than the Hubble time, due to local densities. BH seeds form if their parent gas particle match the criteria required for star formation] and also maintain zero metallicity. [Stinson 2006 for star formation details] A probability of $\chi_{seed}$ = 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle. This probability was chosen to match the predicted occupation probability of BH seeds at z ~ 3. [Volonteri 2008] This circumvents the Soltan arguments wherein mergers alone feed BHs almost entirely without allowing for accretion growth. This method is nearly consistent the theories of direct collapse black holes from gas (Couchmann \& Rees 1986, Abel 2002, Bromm \& Larson 2004) and Population III star black hole formation (Loeb \& Rasio 1994, Eisentstein \& Loeb 1995, Koushiappas 2004, Begelmann 2006, Lodato \& Natarajan 2006). BH seed formation ends at z ~ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae. The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation. Should two BHs form within a softening length, the BHs merge into one with a mass equal to the sum of both BH seed masses. BHs formation is dependent only on their local environment, neglecting any large-scale properties of the host halo. Black holes are not fixed within their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy. Nevertheless, BHs are kept near their host centers by choosing dark matter particles masses in high-resolution regions to be on the same order as gas particle masses which minimizes two-body interactions. [Zolotov 2012, Bellovary et. al. 2010 for all of paragraph]

	Black hole mergers can occur when they meet two criteria. First, the black holes must be within twice the softening length of each, and they must also satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$,  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them. In addition to gaining mass via merger, black holes may also accrete gas via the Bondi-Hoyle method:
\begin{equation}
\dot{M} = \frac{4 \pi \alpha G^2 M^{2}_{BH} \rho}{(c^{2}_{s} + v^2)^{3/2}},
\end{equation}

which is proportional to the accretion rate of gas and assumes $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ for the radiative efficiency. The efficiency $\epsilon _f = 0.03$ is where the feedback energy couples to gas, "which is distributed over the SPH kernel as thermal energy to the 32" nearest gas particles. [Look into this. Confused.] Though other groups (such as Sijacki,2007, Di Matteo 2008) use a higher value for this efficiency, $\epsilon _f = 0.05$, we've found this increased efficiency overpowers the feedback and highly limits gas accretion. Using $\epsilon _f = 0.03$, the MBHs are in better agreement with the MBH-host galaxy scaling relations, e.g. M$_{BH}$-$\sigma$ and M$_{BH}$-M$_{bulge}$. This efficiency value is a simulation parameter used in subgrid feedback models, but does not represent a specific physical quantity, and therefore some variation among codes is expected. Finally, as this work's main concern is the relative accumulation of gas through various accretion methods and not the total value of accreted gas mass, these results are not highly sensitive to adjustments in the feedback implementation.

@@

	The Amiga Halo Finder identifies all of the galaxies in the simulations by identifying the virial radii of the halos based on an overdensity using the criterion for a flat universe. (Amiga Halo Finder paper REF] We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.

	In this analysis, we use the method utilized in \cite{Brooks2009} to trace gas particles from their origin, through their journey into the galaxy, and determine their position within the SMBH or its host. \cite{Brooks2009} studied the accretion of gas by galaxies in cosmological simulations with a focus on gaseous and stellar buildup of their disks. We use this method to trace the gas particles from their initial location to their moment of halo entry and, for some of the particles, into the SMBH. Utilizing this specific method allows us to determine the state of the gas as it enters the galaxy, by determining the method by which it enters the primary galaxy. By determining the method of entry, we can better track the "types of gas" fueling the SMBH resevoir. \\

[Kelly question: If the fingerprint of the fuel inflow is unique, can the angiular momentum of the gas infer spin?]

>>>>

%\documentclass[]{emulateapj}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{n.nicole.sanchez@vanderbilt.edu}

@@

%\citep[for example; ][at the end of the line]{Bellovary2010,Tremmel2015,Fu2008}
 %\S\ref{sec-intro}

Supermassive black holes (SMBHs) are thought to exist in almost all massive galaxies. \citep{Kormendy2013} In the canonical picture of BH growth, these black holes may become active galactic nuclei (AGN) during periods of high accretion and wane in periods of quiescence. \citep{Volonteri2012,Alexander2005,Papovich2006} The host galaxy's size, star formation rate, and other environmental effects may help to influence the growth of the black hole residing at its center; however, there are still uncertainties concerning the relationship between these SMBHs and their much larger host galaxies, as well as how they grow and evolve together. \citep[Need more refs here; how many? Should I cite as many people as Jillian does? More?]{Fu2008}

The M$-\sigma$ relation, which relates the SMBH's mass and the velocity dispersion of the host galaxy's central stellar population, gives some insight into the complex interplay between these objects. \citep{Kormendy2013} A prominent trend appears, as SMBHs tend to scale with the velocity dispersion of the host galaxy bulge. % For my thesis: A prominent trend appears as SMBHs tend to scale with the spheroidal center of their host galaxies; i.e. less massive SMBH reside in galaxies with less disperse bulges, and more massive SMBH live in galaxies with larger velocity dispersions in their bulges. 
The tightness of the relation is significant and can be seen over several orders of magnitudes in velocity dispersion and black hole mass. \citep{Mcconnell2013,Kormendy2013,Merritt2001} Scatter exists among the low mass galaxies and a deviation may appear at the high mass end, where overmassive BHs may reside. \citep{Moster2010,Natarajan2011} However, scatter in less massive galaxies may imply that there are several channels of black hole growth at play in the low mass end of the relation. \citep{Micic2007,Volonteri2009,Graham2014} One standard explanation for the M$-\sigma$ relation lies in galaxy mergers, which build up galaxies, feed SMBHs, and assemble bulges. \citep{DiMatteo2005} [They are theory, need observational ref?] These large, active mergers are thought to create feedback from the SMBH which affects the structure of the galaxy. In addition to the M$-\sigma$, other relations between the SMBH and its host have been well studied, making it clear that, though these objects have many orders of magnitude between their sizes, a complex interplay still exists.

%[CITE FOR THEORY: Springel and Dimatteo; cite when we discuss why m-sigma happens]
%McConnell and Ma have the prettiest M-sigma relation, but there are two camps: Kormendy and Ferrarese & Merritt who must both be cited.
%Check with Kelly: Which Vanden, Bosch, Emsellem, and Prija papers she would recommend.

@@

The M$_{\rm BH}$-bulge luminosity relation was first implied by the work of \cite{Dressler1988}. \cite{Dressler1989} first proposed the correlation and it was first illustrated by \cite{Kormendy1993}. The M$_{\rm BH}$-bulge mass relation followed and was determined via ground based observations by \cite{Magorrian1998} and was around M$_{\rm BH}$ $\sim$0.005 M$_{\rm bulge}$; however, this relation was characterized by a lot of scatter and its reliability waned due to selection biases.  Follow up examinations by others using HST observations constrained the M$_{\rm BH}$/M$_{\rm bulge}$ fraction to between about 0.0013 and 0.0023 \citep{Merritt2001a,McLure2001,Marconi2003}.

Major mergers between massive galaxies are thought to be efficient fueling mechanisms for bright AGN. The large influx of material due to tidal torques from the merger causes bursts of star formation and helps funnel gas directly into the center where the SMBH resides. \citep{Richards2006,Reddy2008,Hopkins2010} Additionally, the most massive, highest-luminosity AGN (i.e. quasars) reside in incredibly luminous infrared galaxies where star formation is abundant, signifying that major mergers may have recently occurred. \citep{Treister2012} Distorted morphologies are often characteristics of quasar hosts, and companions can also be present around quasars, both of which are evidence that strengthen the possibility of a recent merger having affected their lifetimes.

In many less massive AGN, however, there is a clear lack of distorted morphologies, close neighbors, and/or other obvious merger evidence.  \citep{Ryan2007,Hicks2013} It is also important to note that many of these AGN exist in spiral galaxies, which are unlikely to have been recently disturbed by major mergers. \citep{Schawinski2011,Kocevski2011} Nevertheless, some evidence suggests \citep{Governato2009} that disturbed galaxies may reform a disk quickly, even if their history is characterized by many mergers. More recently, \cite{Treister2012} has suggested that only the highest luminosity AGN require fueling via major mergers, an effect which seems to scale with luminosity rather than redshift. They found that $\sim$90\% of AGN across all redshifts are fueled by various other mechanisms which may include minor mergers, flybys, and smooth accretion, whereby gas is directly accreted via large filaments from the ambient intergalactic medium. Secular processes, including bar formation and disk instabilities, may also be prominent forms of accretion for these SMBHs. \citep[][Possibly cite Graham, which?]{Kormendy2013}

Smooth accretion of unshocked gas seems a likely candidate for fueling these low mass galaxies. Filaments of unshocked gas may fuel until the galaxy halo reaches a total (virial) mass near 10$^{11} M_{\odot}$; once in more massive halos, the gas will shock heat to the virial temperature of the halo. Nevertheless, filaments of unshocked gas may still penetrate shocked regions allowing unshocked gas to still flow into the galaxy. \citep{Brooks2007,Dekel2009,Keres2005}

% For my thesis: The unshocked flow filaments that feed thses galaxies are dependent on the galaxy's mass. Smoothly accreted gas will fuel through unshocked gas filaments until the galaxy halo reaches a a mass near 10$^{11} M_{\odot}$. Once the galaxy's mass is greater than this threshold, the mass will reach the virial radius of the halo and the rapid increase in temperature within the radius causes the gas to shock as its temperature quickly increases.

It is clear that galaxy hosts grow through variety of channels that depend on mass, environment, and interaction history. Therefore, we would like to understand how these different galaxy evolutionary paths translate into different SMBH fueling mechanisms, and see how they affect the state of fueling gas flowing into the SMBH itself. \cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH at their centers. Using a similar method as \cite{Bellovary2013}, this work compares the fueling mechanisms between two MW mass galaxies and the accretion affecting each of their SMBHs.

We analyze two galaxy simulations that appear similar at z = 0 but have very different merger histories. Our ``active'' galaxy, h258, has a history characterized by many major mergers, while our ``quiet'' galaxy, h277, has a quiescent history dominated by unshocked gas accretion and few minor mergers. While these galaxies have many of the same properties as the Milky Way including mass within the virial radius (M$_{\rm vir}$), stellar mass, and circular velocity (v$_{\rm circ}$), without a deeper examination, we may not recognize the varying histories that distinguish them. We will compare the BH fractions and halo fractions between and within the galaxies to look for clues about SMBH preferential feeding within these galaxies and how their histories lead to such similar structure. %Along these lines, we will also discuss the fueling mechanisms which vary between these galaxies of similar mass due to different merger and formation histories. 
Milky Way-type galaxies host SMBHs on the order of 10$^6$ M, which are likely the most common type of massive black hole, yet little is known about them or how they may grow. By examining the feeding mechanisms of these galaxies, as well as what type of gas feeds their central SMBHs, we will be able to compare the accretion rates between h258 and h277 to determine which accretion methods dominate within the central regions of this class of galaxies.

[Note to self: Do I thoroughly discusses what we think we KNOW about growth/evolution and what is still being DEBATED?]

@@

The cosmological simulations have been run using two smoothed particle hydrodynamics (SPH) N-body tree code: Gasoline \citep[][Stadel 2001, how do I cite a PhD thesis?]{Wadsley2004} and, more recently, Charm N-body GrAvity solver, ChaNGa.

An initial DM-only, uniform resolution 50 comoving Mpc box was used to determine which halos would be selected for zoom-in examination, including the two halos examined in this paper. The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77. The halos h258 and h277  were chosen for their Milky Way-mass, between 6--8 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and their active and quiescent merger histories, respectively. The halos have virial masses defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 [CITE GROSS 1997, how do I cite a Phd paper?] where h258 and h277 have virial masses of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$ and $M_{\rm vir} = 8 \times 10^{11} M_{\odot}$, respectively. A recent binary merger characterizes the h258 halo at z=1, while h277 has its last major merger near z $\sim$ 3. A second ``zoom-in'' high resolution simulation was run for both of these galaxies including gas and star particles using the volume renormalization of \cite{Katz1993}. This technique retains the large volume simulation size at lower resolution while allowing for only the closest few virial radii from the primary halo to be simulated at the highest resolution. By keeping the largest volumes at low resolution, we are able to account for building of angular momentum through the large scale tidal field in tidal torque theory. Both simulations were run from z=150 to z=0.  [Make sure this is true for low res. True for high res]

Gas is allowed to reach a minimum temperature of $\sim$100 K, though cooling via molecular hydrogen or metals is not included. The simulation includes stochastically modeled star formation, including a star formation efficiency parameter of c$^*$ $=$ 0.1 and density threshold (2.5 amu cm$^{-3}$) for gas particles above which they become eligible to form stars; the gas must also be below a temperature threshold of 10$^4$ K. Star particles form along the Kroupa initial mass function \citep{Kroupa2001}. Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the method of \cite{Ostriker1988}. In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant. SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the method of \cite{Raiteri1996}. Both supernova ``blastwave'' radius calculations and supernova (Ia and II) prescriptions are as described in detail by \cite{Stinson2006}. A low-temperature extension to the cooling curve is used to trace metals \citep{Bromm2001}. These methods have proven to adhere to the observed, redshift dependent stellar mass-metallicity relation for galaxies. \citep{Brooks2007,Maiolino2008} These parameters and resolution choice allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation. \citep{Moster2010,Munshi2013} We are confident with these criteria and restraints that we reasonably represent growth in the galaxy and its SMBH.

Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}.

 The aforementioned works have previously demonstrated that realistic galaxy models can be obtained without the use of these advanced features. \citep{Christensen2012}. Though these previous works have not included AGN feedback or its effects, for small to moderate mass galaxies (like those of previous and current studies) our research shows their central supermassive black holes have little affect on the global properties of their hosts and only directly impacts the central region of their galaxy. Therefore, we are confident these simulations are in good accordance with the broad range of properties in current galaxy observations.

 There are still many uncertainties regarding the formation of black holes ``seeds'' and their evolution into the SMBHs we see at the centers of galaxies. Neverthless, we do know there must be some mechanism driving their quick transformation from seeds to quasars that can be seen at z $\sim$ 6. \citep{Fan2001} Our method of BH formation is broadly consistent the theories of direct collapse black holes from pristine, low metallicity gas \citep[][Add Abel 2002]{Couchman1986, Bromm2004} and Population III star black hole formation \citep{Loeb1994, Eisenstein1995, Koushiappas2004, Begelman2006, Lodato2006}. While this method allows the BH formation process to remain physically motivated, the choice of BH seeding method is not terribly important as our focus remains on the dynamic evolution of the seeds, which is not dependent on their initial mass (10$^5$ M$_{\odot}$ for the direct collapse scenario and 100 M$_{\odot}$ for the first stars). BH seeds form if their parent gas particle match the criteria required for star formation and also maintain zero metallicity. \citep{Stinson2006} A probability of $\chi_{\rm seed}$ = 0.01 is applied to determine whether a gas particle (with the above specifications) will become a BH seed with a mass of M$_{\rm BH}$ = 2.28 $\times$ 10$^5$ M$_{\odot}$, the same mass as its parent gas particle. This probability was chosen to match the predicted occupation probability of BH seeds at z $\sim$ 3. \citep{Volonteri2008} This circumvents the Soltan argument wherein mergers alone are not the primary feeders of BHs, allowing for accretion growth to dominate \citep{Soltan1982}.  BH seed formation ends at z $\sim$ 3.5 due to the dilution of pristine gas by efficient metal diffusion expected after the first population of supernovae. The requirement that BH seeds must form from zero metallicity gas particles also causes BH formation to be constrained in areas of early star formation bursts, where the earliest and most massive halos are expected to form in the simulation. BH formation is dependent only on their local environment, neglecting any large-scale properties of the host halo. Black holes are not fixed within the center of their host, allowing them to be dynamically affected by mergers and other perturbations within the galaxy. Nevertheless, BHs are kept near their host centers by choosing dark matter particles masses in high-resolution regions to be on the same order as gas particle masses which minimizes two-body interactions. \citep{Bellovary2010,Zolotov2012}

Black hole mergers can occur when they meet two criteria. First, the black holes must be within twice the softening length of each, and they must also satisfy $(1/2) \delta v^2 < \delta a \cdot \delta r$,  where $\delta v$ and $\delta a$ are the velocity and acceleration differences between the two black holes and $\delta r$ is the distance separating them. In addition to gaining mass via merger, black holes may also accrete gas via the Bondi-Hoyle method:
\begin{equation}
\dot{M} = \frac{4 \pi \alpha G^2 M^{2}_{\rm BH} \rho}{(c^{2}_{s} + v^2)^{3/2}},
\end{equation}

which is proportional to the accretion rate of gas and assumes $\epsilon _r = 0.1$ and $\epsilon _f = 0.03$ for the radiative efficiency and feedback efficiency. The efficiency $\epsilon _f = 0.03$ is where the feedback energy couples to gas and is distributed across the SPH kernel in the form of thermal energy to the closest 32 gas particles. Though other groups \citep{Sijacki2007,DiMatteo2008} use a higher value for this efficiency, $\epsilon _f = 0.05$, we've found this increased efficiency overpowers the feedback and highly limits gas accretion. Using $\epsilon _f = 0.03$, the MBHs are in better agreement with the MBH-host galaxy scaling relations, e.g. M$_{\rm BH}$-$\sigma$ and M$_{\rm BH}$-M$_{\rm bulge}$. This efficiency value is a simulation parameter used in subgrid feedback models, but does not represent a specific physical quantity, and therefore some variation among codes is expected. Finally, as this work's main concern is the relative accumulation of gas through various accretion methods and not the total value of accreted gas mass, these results are not highly sensitive to adjustments in the feedback implementation.

@@

The cosmological simulations were first run using the smoothed particle hydrodynamics (SPH) N-body tree code Gasoline \citep[][Stadel 2001, how do I cite a thesis?]{Wadsley2004}, with a force resolution of 320 pc and the gas, dark matter, and star particles having a masses of 2 $\times$ 10$^5$ M$_{\odot}$, 3 $\times$ 10$^5$ M$_{\odot}$, and 7 $\times$ 10$^4$ M$_{\odot}$, respectively.

	%FOR THESIS ONLY: [Jillian's paper includes a table of simulation properties. Should I create one as well? I feel like yes.]

@@

The Amiga Halo Finder identifies all of the galaxies in the simulations by identifying the virial radii of the halos based on an overdensity using the criterion for a flat universe. [REF] We select the primary halo by determining the most massive galaxy at z=0 and locating the central SMBH.

In this analysis, we use the method utilized in \cite{Brooks2009} to trace gas particles from their origin, through their journey into the galaxy, and determine their position within the SMBH or its host. \cite{Brooks2009} studied the accretion of gas by galaxies in cosmological simulations with a focus on gaseous and stellar buildup of their disks. We use this method to trace the gas particles from their initial location to their moment of halo entry and, for some of the particles, into the SMBH. Utilizing this specific method allows us to determine the state of the gas as it enters the galaxy, by determining the method by which it enters the primary galaxy. By determining the method of entry, we can better track the origins of the gas fueling the SMBH resevoir.

[Kelly question: If the fingerprint of the fuel inflow is unique, can the angular momentum of the gas infer spin?]

We then trace the SMBH back through time, determining its host halo in each snapshot. Gas particles that are part of merger events are traced back through every merger they've encountered--within their merger trees--to determine their origin and which other halos each gas particles previously inhabited.
